% template created by: Russell Haering. arr. Joseph Crop
\documentclass[12pt,letterpaper]{article}
\usepackage{anysize}
\marginsize{2cm}{2cm}{1cm}{1cm}

\begin{document}

\begin{titlepage}
    \vspace*{4cm}
    \begin{flushright}
    {\huge
        ECE 375 Lab 1\\[1cm]
    }
    {\large
        Introduction to AVR Tools
    }
    \end{flushright}
    \begin{flushleft}
    Lab Time: Wednesday 5-7
    \end{flushleft}
    \begin{flushright}
    Jacques Uber
    \vfill
    \rule{5in}{.5mm}\\
    TA Signature
    \end{flushright}

\end{titlepage}

\section{Additional Questions}
\begin{enumerate}
    \item
    Go to the lab webpage and download the template write-up. Read it thoroughly and get familiar
    with the expected format.  Specifically look at the included source code. What type of font is
    used? What size is the font? From here on when you include your source code in your lab write-up
    you must adhere to that font type and size.


    The font looks like Computer Modern Teletype. It's displayed using the `verbatim` tag. It is 12pt font.

    \item
    Take a look at the code you downloaded for today’s lab. Notice the lines that begin with .def and
    .equ followed by some type of expression. These are known as pre-compiler directives. Define
    pre-compiler directive. What is the difference between the .def and .equ directives (HINT: see
    section 5.1 of the AVR Starter Guide given on the lab webpage).

    \begin{verbatim}.equ\end{verbatim}
    This directive set's a "symbol to an expression."
    \begin{verbatim}.def\end{verbatim}
    This directive defines a "symbolic name on a register."

    \item
    Take another look at the code you downloaded for today’s lab. Read the comment that describes
    the macro definitions. From that explanation determine the 8-bit binary value of the following
    expressions. Note: the numbers below are decimal values.

    \begin{enumerate}
        \item
            \begin{verbatim}
            >>> 1 << 2
            4\end{verbatim}
        \item
            \begin{verbatim}
            >>> 2 << 1
            4
            \end{verbatim}
        \item
            \begin{verbatim}
            >>> 4 >> 1
            2
            \end{verbatim}
        \item
            \begin{verbatim}
            >>> 1 << 4
            16
            \end{verbatim}
        \item
            \begin{verbatim}
            >>> 6 >> 1 | 1 << 6
            67
            \end{verbatim}
    \end{enumerate}

\end{enumerate}

\end{document}
